Variability in upwelling patterns across the Benguela upwelling systems

### 2019-10-08 Write_up/Paper1_writeup.Rmd
updated

Lamberts Bay & 10000 & 3.28725 \\
Lamberts Bay & 20000 & 2.92200 \\
Lamberts Bay & 30000 & 2.92200 \\
Lamberts Bay & 40000 & 2.55675 \\
Lamberts Bay & 50000 & 1.82625 \\
Port Nolloth & 10000 & 2.55675 \\
Port Nolloth & 20000 & 2.55675 \\
Port Nolloth & 30000 & 1.46100 \\
Port Nolloth & 40000 & 1.09575 \\
Port Nolloth & 50000 & 1.09575 \\
Saldanha Bay & 10000 & 3.28725 \\
Saldanha Bay & 20000 & 4.38300 \\
Saldanha Bay & 30000 & 4.01775 \\
Saldanha Bay & 40000 & 2.92200 \\
Saldanha Bay & 50000 & 2.92200 \\
Sea Point & 10000 & 3.28725 \\
Sea Point & 20000 & 3.65250 \\
Sea Point & 30000 & 4.01775 \\
Sea Point & 40000 & 3.28725 \\
Sea Point & 50000 & 2.19150 \\

@@

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{The absolute cumulative intensity (°C.day) for the sites located within the Benguela upwelling system using the SACTN dataset. The site column gives the name of the site. Tempertures were collected at the coastline and not at different distances from the coastline. The cumulative intensity expects as absolute magnitudes rather than relative seasonal climatology} \\

@@

Lamberts Bay & 1.09575 \\
Port Nolloth & 1.09575 \\
Saldanha Bay & 0.36525 \\
Sea Point & 1.09575 \\

>>>>

Lamberts Bay & 10000 & 3.29 \\
Lamberts Bay & 20000 & 2.92 \\
Lamberts Bay & 30000 & 2.92 \\
Lamberts Bay & 40000 & 2.56 \\
Lamberts Bay & 50000 & 1.83 \\
Port Nolloth & 10000 & 2.56 \\
Port Nolloth & 20000 & 2.56 \\
Port Nolloth & 30000 & 1.46 \\
Port Nolloth & 40000 & 1.10 \\
Port Nolloth & 50000 & 1.10 \\
Saldanha Bay & 10000 & 3.29 \\
Saldanha Bay & 20000 & 4.38 \\
Saldanha Bay & 30000 & 4.02 \\
Saldanha Bay & 40000 & 2.92 \\
Saldanha Bay & 50000 & 2.92\\
Sea Point & 10000 & 3.29 \\
Sea Point & 20000 & 3.65 \\
Sea Point & 30000 & 4.02 \\
Sea Point & 40000 & 3.29 \\
Sea Point & 50000 & 2.19 \\

@@

<!-- \def\tiny{\@setfontsize\tiny{10pt}{11pt}} -->
\begin{tiny}
\begin{center}
\setlength\tabcolsep{3pt}
\begin{longtable}{|r|r|p{2cm}|}
\caption{The cumulative intensity (°C x day) for the sites located within the Benguela upwelling system using the SACTN dataset. The site column gives the name of the site. Tempertures were collected at the coastline and not at different distances from the coastline.} \\

@@

Lamberts Bay & 1.10 \\
Port Nolloth & 1.10 \\
Saldanha Bay & 0.37 \\
Sea Point & 1.10 \\
